Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Styled the code
Removed a commented out section
Styled the code chunk and reworded the caption

knitr::kable(outcomes_overall, caption = 'Model outcomes by collaboration type', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position', 'repeat_header'), font_size = 8)
```

>>>>

knitr::kable(outcomes_overall, 
             caption = 'Outcomes studied by the collaboration types', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'HOLD_position', 
                                                    'repeat_header'), 
                                  font_size = 8)
```
